An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-10 DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
updated author affiliations

\author{Dimo Brockhoff and Nora Touati-Moungla}

\address{Laboratoire d'Informatique, \'{E}cole Polytechnique, 91128 Palaiseau Cedex, France\\
\{Brockhoff, touati\}@lix.polytechnique.fr}

>>>>

\author{Dimo Brockhoff}
\address{INRIA Lille - Nord Europe, DOLPHIN team, 59650 Villeneuve d'Ascq, France\\
{\upshape \url{dimo.brockhoff@inria.fr}}}

\author{Nora Touati-Moungla}
\address{Laboratoire d'Informatique, \'{E}cole Polytechnique, 91128 Palaiseau Cedex, France\\
{\upshape \url{touati@lix.polytechnique.fr}}}
